Classifier Explanation

### 2019-05-08 Paper/paper.Rmd
Added more documentation for XGBoost, I also clarified the use of the fastText classification model.

To use our model, we fed a set of tweets into a PCA model. The output of the PCA model (unsupervised) was then fed into an XGBoost model (supervised). Simultaneously, we fed the same set of tweets into a fastText classification model (supervised). The frankenstien model then compares predictions of the XGBoost and fastText models, and makes a final prediction. I believe that the idea behind this "frankenstein model" is to use the perspectives of various styles of models to gain an accurate consensus on the data -- somewhat similar to the concept behind random forests.

@@

# The fastText Sub-Model
## Overview
In this section, we will document how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.

@@

Decision Trees: https://www.youtube.com/watch?v=7VeUPuFGJHk
Random Forests: https://www.youtube.com/watch?v=J4Wdy0Wc_xQ
More Random Forests: https://www.youtube.com/watch?v=nyxTdL_4Q-Q
Cross Validation: https://www.youtube.com/watch?v=TIgfjmp-4BA
Boostrap Aggregating (Bagging): https://www.youtube.com/watch?v=2Mg8QD0F1dQ
MIT lecture on Boosting: https://www.youtube.com/watch?v=UHBmv7qCey4

>>>>

To use our model, we fed a set of tweets into a fastText word representations model (unsupervised). After summarizing the ouput of this model, we take the fastText model output and send it through a PCA model. The output of the PCA model (unsupervised) was then fed into an XGBoost model (supervised). The XGBoost model then compares predictions of the PCA and fastText models, and makes a final prediction. I believe that the idea behind this "frankenstein model" is to use the perspectives of various styles of models to gain an accurate consensus on the data -- somewhat similar to the concept behind random forests.

@@

In our repository, you will also find that we train and test a fastText classification model (supervised). This model is simply another attempt to create a classification model, and can be thought of as a baseline comparison to the frankenstien model.

# The fastText Classification Model
## Overview
In this section, we will document how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.

@@

XGBoost Documentation: https://xgboost.readthedocs.io/en/latest/R-package/xgboostPresentation.html
Decision Trees: https://www.youtube.com/watch?v=7VeUPuFGJHk
Random Forests: https://www.youtube.com/watch?v=J4Wdy0Wc_xQ
More Random Forests: https://www.youtube.com/watch?v=nyxTdL_4Q-Q
Cross Validation: https://www.youtube.com/watch?v=TIgfjmp-4BA
Boostrap Aggregating (Bagging): https://www.youtube.com/watch?v=2Mg8QD0F1dQ
MIT lecture on Boosting: https://www.youtube.com/watch?v=UHBmv7qCey4
